---
title: "Chemistry of Stream Water from the Luquillo Mountains."
author: "McDowell, William H."
format: html
---

Load all the packages we need to use
```{r setup, include=FALSE}
library(tidyverse)
library(janitor)
library(here)
library(tidyr)
library(dplyr)
library(lubridate)
library(usethis)
library(flowchart)
```

Loading Files
```{r}
BQ1 <- read_csv(here("data", "QuebradaCuenca1-Bisley.csv"))
BQ2 <- read_csv(here("data", "QuebradaCuenca2-Bisley.csv"))
BQ3 <- read_csv(here("data", "QuebradaCuenca3-Bisley.csv"))
prm <- read_csv(here("data", "RioMameyesPuenteRoto.csv"))
```

Based on the caption of figure 3, write down the steps you think will be necessary to reproduce figure 3.
Create a flow chart of how the steps fit together. Things to consider include:

How will you get the data into R?
  - Loading library such as tidyverse & here packages and use `read_csv()` function to get data into R
  
How will you clean up the data?
  - Might require to `group_by()` the years along with each soil types
  - For example, we will make summary statistics of sum / avg of all the years from 1988 to 2020 potassium, nitrate-N, magnesium, calcium, and ammonium-N concentrations in Puerto Rico streams
  - Join all BQ1 through BQ3 summarized datasets (join by Sample_Dates?)
  
Are any processing or modeling steps required?
  - Ggplot
    - x-axis = Years
    - Y-axis = All the concentrations of minerals
    - geom_lines() + geom_smooth() + scatterplots 
    - Specific line for Hurricane Hugo
    - Facet wrap of each concentrations -> Patchworks
    - Labels
    
  
What are your outputs?
  - We should be able to recreate the same visualization of all the information and data that is given by the EDI
  
